The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-27 paper.tex
integrated neuro stuff in 2.2.2

\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\}

@@

This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it. This holds important implications for the resulting interaction with the system, the user experience, and the acceptance. Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} A similar finding is described in \cite{hegel_understanding_2008}. In a user study, the authors found that participants implicitly attributed human-like qualities, such as mental states, to their non-human interaction partner. This finding was evident on a neuro-physiological level as well as behavioral level. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :)}}

In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior. This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}. A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.

@@

Why do we think that anthropomorphic projections are likely to change over time
and with growing experience a person has with a robot? The underlying process in
anthropomorphism is understood as reasoning about and perceiving something
non-human, and unknown or unfamiliar based on one's representation of the
familiar and well-known concept of being human (or one-self). The basic
operations underlying inductive inference are the acquisition of knowledge, the
activation or elicitation of knowledge, and the application of activated
knowledge at the time of the judgment \cite{epley_when_2008}. According to Epley
\textit{et al.}, the application includes attempts to correct, adjust, or
integrate less accessible information into a more automatically activated
default representation. This process can be seen as a process of correction, and
thus, it is often insufficient leaving final judgments biased in the direction
of the initially activated representation. As a person's knowledge base changes
/ evolves constantly with newly acquired things, or growing experiences with a
robot, etc., it is likely that the "need to anthropomorphize" a robot decreases
over time. First, because of the evolved knowledge about it, and second because
one has familiarized oneself with it. Consequently, the robot should become more
predictable and more familiar to the human user and inferences about it can be
made based on the acquired knowledge.  /fxfatal{confusing paragraph...needs
reformulation. Could also be turned into a section introduction instead of a
subsection}

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review previously
published~\cite{fink_anthropomorphism_2012} and field
experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
not always the same but evolve over time, along with growing interaction and
experience with the robot, similar to how relationships among people evolve
over time \fixme{(cite Hinde, 1988)}. In fact, \cite{kanda_interactive_2004}
also hypothesized that people's attitude toward technological artifacts and
their relationship with them would evolve over time, and they were among the
first who described \emph{novelty effects} during a long-term study with an
interactive robot in a school.

@@

While the model primarily considers \emph{long-term interaction} -- direct
(non-mediated), repeated interaction with the same robot, over an extended
period of time (typically longer than a week), we also formally introduce a
so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
first phase of human-robot interaction, during which a specific increase of
anthropomorphic interactions is observed.

@@

\section{Cognitive Correlates and Neuroscience Perspective}
\label{sec:cognition-neuroscience}

In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
We then discuss more speculative aspects and hypotheses that follow
from the model. These aspects would benefit further investigations and
experimental support.

@@

%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
The neuroscientific study of human-robot interaction is still in its infancy. So far most studies have used robots as a way to investigate humans behavior and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviors and brain processes are influenced by its direct interaction with a robot (add ref, ref). 
We briefly review below the neuroscientific literature relevant to understand the neural basis of anthropomorphism.

%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
Resonance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.

\paragraph{Anthropomorphic response to motor behavior \\}
Resonance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.

There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonance mechanisms.
%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms. %mirror neurons

%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.

\paragraph{Anthropomorphism and social behavior}
In studying emotional perception in a human or a robot face using functional magnetic resonance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties. However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expression, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonance.

However, using electroencephalography another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.

%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie. wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).

Finally, individual tendency to anthropomorphize has been related to the grey matter volume of a brain area involved in mentalizing - the attribution of mental states to other human beings \citet{cullen2013individual, Frith2003}.

Thus it seems that the display of resonance mechanisms for social behavior in a human-robot interaction is less straightforward than for motor behavior and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism . Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}

%\paragraph{Emotions/Empathy}
%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.

In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates. We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
discuss these findings.

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonance mechanisms at the neuronal level.

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}). At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behavior which may reinforce the resonance mechanisms.

@@

This mental process depends on the human understanding of the robot's
inner working, as well as his/her own tendency to anthropomorphize (the
\emph{personality} in ICA factor), but at this
stage, the \emph{perception} of the robot (its shape for instance) and its
intended \emph{purpose} play a less important role. It is mostly a human-centric
process.  The result of this third phase would be an iteratively adapted
cognitive model of the robot. It is also at this last stage that the human might modified its own abilities to anthropomorphize, having built a full cognitive model of the robot and know being able to attribute internal state to the robot.

@@

Common observation of naive people (children or adults) interacting with robots
shows that unexpected behaviors of the robot can have a notable impact on
interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
HRI2013 paper}

>>>>

\paragraph*{Cognitive science research, the mental model theory (Theory of Mind)
and neural correlates of anthropomorphism\\}

@@

This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it. This holds important implications for the resulting interaction with the system, the user experience, and the acceptance. Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} 
A similar finding is described in \cite{hegel_understanding_2008} and
\citet{krach_can_2008}. In a user study using functional magnetic resonnance
imagery (fMRI), the authors found that participants
implicitly attributed human-like qualities, such as mental states, to their
non-human interaction partner. Indeed, from an early age humans develop a
tendency to explain one's own and others'actions in terms of beliefs, desires
and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
intentions and other mental states to others \citep{premack1978_does, leslie_pretense_1987, Frith2003}.
\citet{hegel_understanding_2008} and \citet{krach_can_2008} finding was evident at the behavioral level
as well as on the neuro-physiological level: the more the human-likeness of the
artefactual partner increases, the more brain areas associated with theory of
mind  get activated
\citep{krach_can_2008}. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :)}} 
Implication of human brain area involved in the inference of other's mental
states has also been shown in response to viewing
non-anthropomorphic/non-humanoid robotic gadgets whose behaviour
has been described as unpredictable - but not in response to those whose
behavior was described as predictable- a finding also found at the behavioral
level \citep{Waytz2010}.
Interestingly, the grey matter volume of a brain area related to theory of mind
has been correlated to individual's score of anthropomorphism
\citep{cullen2013individual}.

%\paragraph{Mirror neurons and resonnance behaviors \\}
%
%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.  
%
%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
%
%Interestingly, there are good evidence showing that motor mirror neurons in the
%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms. %mirror neurons
%
%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
%
%The response of the human brain to a social signal perceived on a robot, such as facial
%emotional expression is less evident. 
%
%In studying emotional perception in a human or a robot face using functional
%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
%in response to the robot stimuli than to the human stimuli in emotional brain
%areas known to have mirror properties. However if the subject was asked to
%specifically attend to the emotional content of the stimuli, processing of the
%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
%
%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
%
%
%
%

In sum, this branch of research suggests that anthropomorphism implies that
people thoughtfully develop a mental model of agents in their environment and
that they make inferences about these agents based on what is familiar to them
-- themselves, humans and human behavior. This understanding builds on the
theory of mind,  a
person's ability to attribute mental states to oneself and others. 
%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
We briefly reviewed  neuro-physiological evidence of a link between the tendency
to thoughtfully anthropomorphize and the engagement of brain processes involved
in the attribution of mental states to other humans. The human-likeness quality
of the artefactual agent seems to play a role in the involvement of theory of
mind but also the unpredictable feature of the agent behavior alone seems to be
sufficient.  
%were recently demonstrated at the brain level~\citep{cullen2013individual}.

@@

Why do we think that anthropomorphic projections are likely to change over time
and with growing experience a person has with a robot? The underlying process in
anthropomorphism is understood as reasoning about and perceiving something
non-human, and unknown or unfamiliar based on one's representation of the
familiar and well-known concept of being human (or one-self). The basic
operations underlying inductive inference are the acquisition of knowledge, the
activation or elicitation of knowledge, and the application of activated
knowledge at the time of the judgment \citep{epley_when_2008}. According to Epley
\textit{et al.}, the application includes attempts to correct, adjust, or
integrate less accessible information into a more automatically activated
default representation. This process can be seen as a process of correction, and
thus, it is often insufficient leaving final judgments biased in the direction
of the initially activated representation. As a person's knowledge base changes
/ evolves constantly with newly acquired things, or growing experiences with a
robot, etc., it is likely that the "need to anthropomorphize" a robot decreases
over time. First, because of the evolved knowledge about it, and second because
one has familiarized oneself with it. Consequently, the robot should become more
predictable and more familiar to the human user and inferences about it can be
made based on the acquired knowledge.  /fxfatal{confusing paragraph...needs
reformulation. Could also be turned into a section introduction instead of a
subsection}

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time (during the process of
\emph{adopting} a robot, for instance): we propose to go beyond the traditional
perception of anthropomorphism in robotics as a static feature that once
observed during a short-term interaction reflects a sustaining social effect.
Based on an extensive literature review previously
published~\citep{fink_anthropomorphism_2012} and field
experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
not always the same but evolve over time, along with growing interaction and
experience with the robot, similar to how relationships among people evolve
over time \fixme{(cite Hinde, 1988)}. In fact, \citet{kanda_interactive_2004}
also hypothesized that people's attitude toward technological artifacts and
their relationship with them would evolve over time, and they were among the
first who described \emph{novelty effects} during a long-term study with an
interactive robot in a school.

@@

While the model primarily considers \emph{long-term interaction} -- direct
(non-mediated), repeated interaction with the same robot, over an extended
period of time (typically longer than a week), we also formally introduce a
so-called \emph{novelty effect}~\citep{kanda_interactive_2004} that models the
first phase of human-robot interaction, during which a specific increase of
anthropomorphic interactions is observed.

@@

\section{Cognitive Model}
\label{sec:cognition-neuroscience}

In this section are discussing more speculative aspects and hypotheses that follow
from the model. These aspects would benefit further investigations and
experimental support.
%

%In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
%We then discuss more speculative aspects and hypotheses that follow
%from the model. These aspects would benefit further investigations and
%experimental support.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
%\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
%The neuroscientific study of human-robot interaction is still in its infancy. So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref). 
%We briefly review below the neuroscientific literature relevant to understand
%the neural mechanisms that may underly anthropomorphism. 
%\paragraph{Mirror neurons and resonnance behaviors \\}
%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.  
%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
%Interestingly, there are good evidence showing that motor mirror neurons in the
%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms. %mirror neurons
%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
%The response of the human brain to a social signal perceived on a robot, such as facial
%emotional expression is less evident. 
%In studying emotional perception in a human or a robot face using functional
%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
%in response to the robot stimuli than to the human stimuli in emotional brain
%areas known to have mirror properties. However if the subject was asked to
%specifically attend to the emotional content of the stimuli, processing of the
%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
%Thus it seems that the display of resonance mechanisms for social behaviour when
%viewing a robot is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
%%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism . Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual} 
%However, the studies reviewed above show that the human brain can respond
%equally to a human or a robot stimuli but they do not  directly address the
%question of anthropomorphism. Indeed, although it can contribute to it, neither
%activation of mirror neurons system simulating a perceived action nor influence
%on early brain processies readily imply that the human confers a humanlike mental
%state to the robot and thus can not be sufficient to infer anthropomorphism 
%%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie. wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).
%\paragraph{Neural correlates of theory of mind and antropomorphism\\}
%%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
%%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
%In a more direct study of anthropomorphism, \citep{cullen2013individual} related
%participant's scores of tendency to anthropomorphize to the grey matter
%volume of the left temporal junction, a brain area involved in mentalizing,
%that is the attribution of mental states to other human beings (theory of mind) \citep{Frith2003}. 
%Of note, \citet{Waytz2010} showed that the more an artifical agent behaved
%unpredictably, the more subjects tend to attribute it a mind and the more the
%ventro medial prefrontal cortex (VMPFC), key area for sociocognitve processes
%and especially egocentric mentalizing about similar others, gets activated.
%%\paragraph{Emotions/Empathy}
%%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance. 
%In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates. We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
%discuss these findings.

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.

%mediated by the motor and emotional resonnance mechanisms at the neuronal level.

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}). 
%At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.

@@

This mental process depends on the human understanding of the robot's
inner working, as well as his/her own tendency to anthropomorphize (the
\emph{personality} in ICA factor), but at this
stage, the \emph{perception} of the robot (its shape for instance) and its
intended \emph{purpose} play a less important role. It is mostly a human-centric
process.  The result of this third phase would be an iteratively adapted
cognitive model of the robot. It is also at this last stage that the human might
modified its own abilities to anthropomorphize, having built a full cognitive
model of the robot and know being able to attribute internal state to the robot
through his theory of mind.

@@

Common observation of naive people (children or adults) interacting with robots
shows that unexpected behaviors of the robot can have a notable impact on
interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
HRI2013 paper}
This is supported by the results from \citet{Waitz2010} seen in section
\ref{sec:explanations} that people attribute more easily anthropomorphic
features to artefacts when they have unpredictable behaviors.
